Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$

### 2015-05-08 formalwriteup.tex
revised complete intersection argument

%mention previous results [BEG],[CE],[GLOR]? ask
%deformation of DAHAs introduced by Etingof-Ginzburg in 2001

@@

@@

 \newtheorem*{thm:main}{Theorem \ref{thm:main}}
\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. The maximal ideal $J$ is generated by the coefficients of $z^p$ in the formal power series \\
$$F_a=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. 
\end{thm:main}

@@

In this paper we consider the case where the characteristic of $K$ divides $n$. This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}. In that case the generators of the ideal $J$ were the residues at infinity of $\frac{1}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c$ for each $a$. %write as proposition
To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$. The formal power series would be $\frac{1}{z^{p+1}}\frac{1}{1-x_az}\prod_{j=0}^{n-1} (1-x_jz)^c$, with the corresponding generator as the coefficient of $1/z$. We simplify and truncate the formal power series so we can define it in positive characteristic.

@@

We let $g=\prod_{j=0}^{n-1} (1-x_jz)$. Let $F_a$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.

@@

\begin{proposition}\label{prop:ann} Let $f_a$ be the coefficient of $z^p$ in the power series $F_a$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
\end{proposition}

@@

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$ for all $0 \le i < n-1$. Let $F =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. Note that $F$ is symmetric and $F_a=\frac{F}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$:

@@

&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F\right)\\

@@

%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k}\right)\\
%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k}\right)\\
%&=F\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)+\\&\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\\&\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)

@@

%Let $U=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$; clearly $z^p \mid U$ so all coefficients before that are $0$. The $z^p$ term is $\binom{c}{0}(-1)^0 $

Let $G_i=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right)$. Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.

We also see that:

\begin{align*}
\frac{\partial F_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_1}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_1}{1-x_0z}\\
\end{align*}

and that:

\begin{align*}
\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_0}{1-x_0z}\\
&=\frac{z}{1-x_0z}F_0+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
\end{align*}

We note that $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$.

\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F}{1-x_0z}-\frac{F}{1-x_iz}\right)\\
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F\\
&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F\\
&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F\\
&=\frac{z}{1-x_iz}F_0\\
\end{align*}

We recall that we need only consider the action of $D_1-D_0$ on $F_0$. We consider $D_0F_0, D_1F_0$ separately first. We see that $D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.

\begin{align*}
D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\frac{G_0}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0-\sum_{j > 0} \frac{zc}{1-x_jz}F_0\\
\end{align*}
\begin{align*}
D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
&=\frac{G_1}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{zc}{1-x_1z}F_0\\
&=\frac{G_1}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0\\
\end{align*}

It is then easy to see that $(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0$.

@@

We see easily that $\frac{\partial g}{\partial z} = g \sum_j \frac{-x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$:

\begin{align*}
\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right)
\end{align*}

Let $V=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right)$. Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$.

From this it follows that:

\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F\\
&=\frac{V}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\frac{x_0}{(1-x_0z)^2} F\\
&=\frac{V}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0+\frac{x_0}{1-x_0z} F_0\\
\end{align*}

@@

>>>>

%mention previous results [BEG],[CE],[GGOR]? ask
%deformation of DAHAs introduced by Etingof-Ginzburg in 2001

@@

For a formal power series or Laurent series $r(z)$, we write the coefficient of $z^\ell$ in $r$ as $[z^\ell]r(z)$.

@@

 \newtheorem*{thm:main}{Theorem \ref{thm:main}}
\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series $$F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. 
\end{thm:main}

@@

In this paper we consider the case where the characteristic of $k$ divides $n$. This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.

\begin{proposition}[\cite{CE}, Proposition 3.1] Let the characteristic of $k$ be $0$ and set $c=p/n$. The ideal $J \subseteq A$ where $A$ is the polynomial representation of $\HH_{\hbar,c}(\h)$ is generated by $\Res_\infty\left[\frac{dz}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c\right]$ for $a=0,\dots,n-2$.
\end{proposition}

To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$. The formal power series would be $\frac{1}{z^{p+1}}\frac{1}{1-x_az}\prod_{j=0}^{n-1} (1-x_jz)^c$, with the corresponding generator as the coefficient of $1/z$. We simplify and truncate the formal power series so we can define it in positive characteristic.

@@

We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$. Let $F_a(z)$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a(z)=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.

@@

\begin{proposition}\label{prop:ann} Let $f_a=[z^p]F_a(z)$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
\end{proposition}

@@

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $$\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$$ for all $0 \le i < n-1$. Let $$F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).$$ Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have

@@

&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\

@@

%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\

@@

%Let $G_i=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$. Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.

We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$

We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$.

\begin{align*}
\frac{\partial F_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
\end{align*}
\begin{align*}
\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.\\
\end{align*}

We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that

\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
&=\frac{z}{1-x_iz}F_0(z).\\
\end{align*}

We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that $$D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.

\begin{align*}
D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
\end{align*}
\begin{align*}
D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).\\
\end{align*}

It is then easy to see that $$(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.$$

@@

We see easily that $$\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.$$ We now consider $\frac{\partial F}{\partial z}$.

\begin{align*}
\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}

%\begin{align*}
%\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\prod_{i=0}^{n-1} \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\\
%&=\sum_{i=0}^{n-1}\left(\left(\sum_{k=1}^{p-1} k\binom{c}{k}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left((1-x_iz)\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} -cx_i\binom{c}{k}(-1)^{k}x_i^{k}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\\
%\end{align*}
%
%Let $V=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)$. Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$. 
%

We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$

From this it follows that

\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
\end{align*}

@@

We will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.

We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$; then since $\sum_{i=0}^{n-1} x_i=0$ we have $\sum_{i=0}^{r-1} m_iy_i=0$.

Then $g(z)=(1-y_iz)^{m_i}$. Recall $$F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.$$

We assume that $y_i \ne 0$ for all $i$.

Define $$a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).$$ Recall that we showed $$F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)$$ where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$. We then see that

\begin{align*}
a'(z)&=\frac{d}{dz}\left(\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z)\right)\\
&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F'(z)+\sum_{j=0}^{r-1}\frac{y_j}{(1-y_jz)\prod_{i=0}^{r-1}(1-y_iz)}F(z)\\
&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}\left(V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}a(z)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\left(\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)\right)\\\end{align*}
